Humann2 bar plot by myself

### 2019-10-17 scripts/09_barplot_myself.Rmd
update

# top 8
n <- 8
toppw <- names(mean_s)[1:n]

@@

# now reduce the abundance to 9 rows, the top 8 and "other"

@@

```{r}
# load the table that has the unique sig pathways
sigpw <- read_csv('../data/unique_sig_pathway.csv')

# find how many species total it has in all of the lefse sig pathways
siglefse <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_stratified_reordered.tsv') %>% 
  filter(str_detect(pathway,  paste0(pw$pwid, collapse = '|'))) %>% 
  separate(X1, into = c('pwid','taxa'), sep = '\\|')

>>>>

# top n (variable) including unclassified
n <- floor(length(mean_s)*0.15) 
toppw <- names(mean_s)[1:n]

@@

# now reduce the abundance to 9 rows, the top 8 and "other" (the current will work if the df has >= 9 rows)

@@

```{r}
# load the table that has the unique sig pathways
sigpw <- read_csv('../data/unique_sig_pathway.csv') %>% 
  # grab the pw id which is gonna be able to match the rownames in the stratified table
  mutate(pwid = str_extract(pathway, '^.+_PWY|^PWY_\\d{3,4}'))  %>% 
  mutate(pwid = str_replace_all(pwid, '_', '-'))

# find how many species total it has in all of the lefse sig pathways
siglefse <- stratified %>% 
  filter(str_detect(pathway,  paste0(sigpw$pwid, collapse = '|'))) %>% 
  separate(pathway, into = c('pwid','taxa'), sep = '\\|')
